Modelling the Lymphatic Metastatic Progression Pathways of OPSCC \\ from Multi-Institutional Datasets

### 2023-12-19 src/tex/ms.tex
[showyourwork] overleaf sync

% Title
\title{Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets}

% Author list
\author{Roman Ludwig}
\author{Adrian Schubert}
\author{Dorothea Barbatei}
\author{Lauence Bauwens}
\author{Jean-Marc Hoffmann}
\author{Sandrine Werlen}
\author{Olgun Elicin}
\author{Matthias Dettmer}
\author{Philippe Zrounba}
\author{Bertrand Pouymayou}
\author{Panagiotis Balermpas}
\author{Vincent Grégoire}
\author{Roland Giger}
\author{Jan Unkelbach}

>>>>

% Title
\title{Modelling the Lymphatic Metastatic Progression Pathways of OPSCC \\ from Multi-Institutional Datasets}

% Affiliations
\def \USZ {University Hospital Zurich, Rämistrasse 100, 8091 Zurich, Switzerland}
\def \UZH {University of Zurich, Rämistrasse 71, 8006 Zurich, Switzerland}
\def \ISB {Inselspital Bern, Freiburgstrasse 18, 3010 Bern, Switzerland}
\def \CLB {Centre L\'eon B\'erard, 28 Rue Laennec, 69008 Lyon, France}
\def \KS  {Klinikum Stuttgart, Kriegsbergstraße 60, 70174 Stuttgart, Germany}

% Author list
\author[0000-0001-9434-328X]{Roman Ludwig}
\affiliation{\USZ}
\affiliation{\UZH}

\author{Adrian Schubert}
\affiliation{\ISB}

\author{Dorothea Barbatei}
\affiliation{\CLB}

\author{Lauence Bauwens}
\affiliation{\CLB}

\author[0000-0003-1193-0863]{Jean-Marc Hoffmann}
\affiliation{\USZ}

\author{Sandrine Werlen}
\affiliation{\ISB}

\author[0000-0002-6996-0646]{Olgun Elicin}
\affiliation{\ISB}

\author[0000-0003-0948-1392]{Matthias Dettmer}
\affiliation{\KS}

\author[0000-0001-6223-6113]{Philippe Zrounba}
\affiliation{\CLB}

\author[0000-0002-8060-7827]{Bertrand Pouymayou}
\affiliation{\USZ}

\author[0000-0001-5261-6446]{Panagiotis Balermpas}
\affiliation{\USZ}

\author{Vincent Grégoire}
\affiliation{\CLB}

\author[0000-0002-5574-3210]{Roland Giger}
\affiliation{\ISB}

\author[0000-0002-4275-990X]{Jan Unkelbach}
\affiliation{\USZ}
\affiliation{\UZH}

\correspondingauthor{Roman Ludwig}
\email{roman.ludwig@usz.ch}
